% ************************** Thesis Abstract *****************************
% *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, or Math in Paper Title or Abstract.
%
% Use buzzwords
% Don't use jargon
% Generic to specific
% Pose questions
%
% In de samenvatting komt te staan:
% - Onderwerp-informatie;
% - probleemomschrijving/-analyse;
% - probleemvraag; - onderzoeksmethode;
% - de belangrijkste resultaten kort samengevat;
% - de (belangrijkste) conclusies.
%
\begin{abstract}
Taxi companies have been delivering booking apps as a result of passengers' raising expectations of being presented a list of available cabs with corresponding prices on demand. YourDriverApp is a new white label application developed by taxiID that is set to provide this solution to taxi companies worldwide. Despite the fact that YourDriverApp is new, it still depends on the price calculation functionality of a legacy system, which was not designed with internationalization in mind.



The resulting problem

It was created to process postal codes and addresses to determine the price of a trip, which is impossible for countries without a postal code system.

The price calculation system depends on addresses and postal codes. Some clients live in countries that do not have such a system to begin with.



The problem is that YDA depends on a legacy systems price calculation functionality



on the screen and a potential passenger is presented a list of available vehicle types that may take the passenger to the desired destination.
and prices that correspond with the distance and
needs its own price calculation system

The aim of this study is to determine how such a system can be implemented in a way that is usable by companies all over the world

The research questions are answered by gathering information available in the public domain.

Applying proposals derived from this research

has been researched. Information available in the public domain has been used to answer empirical questions, from which proposals based on good arguments have been made, and


A purely geometrical interpretation of user-defined locations would allow taxi-companies around the world to set up rules so that trip prices could be calculated without depending on distinct postal code systems. Geolocation datatypes provide part of the solution, but the benifits of geometrical definitions are lost when areas intersect. A hierarchy of precedence based rules tied to reusable locations would eliminate these competing rule matches.

A solution is proposed to implement a microservice with a single responsibility of calculating trip prices that is accessible to existing systems and portals in which users can define the pricing rules. The company for which this system is realized requires customers to be able to migrate to the new system without downtime, while keeping the existing rules that determine the prices of taxi trips.

The portals providing users access to company information must integrate a separate user interface allowing pricing rules to be managed. The microservice must be able to authenticate direct requests. The core system manages user and company data, complicating identity management in the microservice. A JSON Web Token would allow user identity to be stored in the payload of the token, thereby delegating authentication to the core system, safeguarding the single responsibility of the microservice.


% In de samenvatting komt te staan:
% - Onderwerp-informatie;
% - probleemomschrijving/analyse;
% - probleemvraag;
% - onderzoeksmethode;
% - de belangrijkste resultaten kort samengevat;
% - de (belangrijkste) conclusies.

\end{abstract}
