\documentclass[11pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Titlepage & table of contents
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}

\input{src/customcommands}

\begin{document}
\input{src/intro/titlepage}

\tableofcontents
\printindex
\newif\ifdraft\drafttrue

% T - topic
% E - explain
% E - example

% Active - The dog bit the man.
% Passive - The man was bitten by the dog.

% Present - Jones presents that the ...
% Past - In 1994, Hilton Hotels Corporation ...
% Future - Jones will find out that …

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Preface
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{src/chapters/preface}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{src/chapters/abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Keywords
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{src/chapters/keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Introduction
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{src/chapters/introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Context
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% - General
% - Structure
% - Clients
%
\section{Context}
taxiID is an Amsterdam based company providing end-to-end cloud solutions for taxi companies. Founded as a startup that successfully introduced smartphone taxi booking in The Netherlands, taxiID offers a wide range of IT solutions to serve the taxi market, including a passenger app, a driver app, administrative panels, and track and trace hardware.

taxiID solutions have proven to be a reliable set of tools for all size businesses. For independent taxi companies with 2 cars or a companies with large fleets, affordable solutions are available. taxiID's goal is to deliver affordable, time-saving solutions for taxi companies to allow for convenient planning and dispatching without requiring local installation.

Tough based in Amsterdam, the development team is located in Medemblik, consisting of two mobile developers, two backend developers, a designer and two project managers.

taxiID's customers are located across the globe. This introduces challenges when developing applications that rely on clearly defined locations and infrastructure of all kinds.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Assignment
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% - Origin of the assignment
% - Description
% - Research question
% - Sub questions
%
\section{Assignment}
% Waar gaat dit hoofdstuk over?


\subsection{Origin of the assignment}
% Waarom deze opdracht?
YourDriverApp (YDA) requires a pricing calculation functionality that is similar to the existing taxiID implementation. All functionalities within the current system align with the clients demands, but some features bring certain difficulties along, for example: region names are too vague for specific database queries. Some features could be abstracted so more possibilities can be implemented, some features are still unimplemented, and some features could be improved along the way.

\subsection{Description}
% Welke problemen moeten worden opgelost
A system must be implemented in which group admins can define pricing rules based on user defined locations and time schedules, that can be used for calculating a passengers trip price, or show prices of different products based on the trip the passenger is about to make. For example: a passenger may book a taxi ride from Utrecht to Schiphol using the passenger app. Available products are presented with their respective prices based on the distance and duration of the trip using the pricing rules that were created by the group admin of a taxi company.

The system must be usable in countries with a poor postal code system. There should be a way for a group admin to describe locations in a way that are precise and consistent with reality, meaning that a defined location should be usable from outside of the system, or at least be interpretable. An example of this requirement would be: a taxi company that operates in Afghanistan. A passenger wants to be picked up on some road near the mountains. How would a group admin describe that location in order to define a price beforehand?

The system should be accessible to other systems, meaning that applications that currently rely on the old system should be able to migrate to the new system. As the old system shouldn't be used for new applications, as it was not designed for this use case, the new system should. It should have a single responsibility, and should be atonomous in that regard.

\subsection{Research question}
% Welke hoofdvraag moet worden beantwoord om de opdracht succesvol af te ronden?
From the description of the problem, one main important question could be derived. How can a generic price calculation system be implemented that is usable across the globe?

\subsection{Sub questions}
% Hoe kunnen we de hoofdvraag opdelen?
Which varieties of address formats exist around the world?

Is it possible to redefine different address formats as a generic address?
- Gps
- Zip code

To what extent do address formats have an impact on performance of a price calculation?


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Review
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% - Which solutions exist
%
\section{Literature Review}
% Waar gaat dit hoofdstuk over?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Proposed Approach
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% - Methods
% - Techniques
%
\section{Chapter 1 - proposed approach}
% Waar gaat dit hoofdstuk over?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Realization
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% - What has been created
%
\section{Realization}
% Waar gaat dit hoofdstuk over?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Conclusion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Conclusion}
% Waar gaat dit hoofdstuk over?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Recommendations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Recommendations}
% Waar gaat dit hoofdstuk over?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{References}
% Waar gaat dit hoofdstuk over?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Glossary
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Glossary}
% Waar gaat dit hoofdstuk over?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Appendices
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Appendices}
% Waar gaat dit hoofdstuk over?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Reflection
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Reflection}
% Waar gaat dit hoofdstuk over?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{thebibliography}{00}
  \bibitem{b0} R. C. Martin, Clean Code: A Handbook of Agile Software Craftsmanship. Pearson Education, August 2008, pp. 4, 5.
  % \bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
  % \bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
  % \bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
  % \bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
  % \bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
  % \bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
  % \bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}

\end{document}
